When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases

### 2018-02-14 paper/paper.tex
Cumulative (review 1)

    \caption{Cumulative number of instances solved as a function of search space size, using four
    graph database datasets, and either VF2 or a simple constraint programming subgraph isomorphism
    algorithm implemented in Gecode. The $x$-axis shows recursive calls, using a log scale, and each
    line ends at the $x$ value where every instance has been solved.}
    \label{figure:biiiig-data}
\end{figure}

>>>>

    \caption{The cumulative number of instances solved as a function of search space size, using four
    graph database datasets, and either VF2 or a simple constraint programming subgraph isomorphism
    algorithm implemented in Gecode. The $x$-axis shows recursive calls, using a log scale, and each
    line ends at the $x$ value where every instance has been solved.}
    \label{figure:biiiig-data}
\end{figure}
